Clustering: A pipeline to analyse time-course gene expression data

### 2019-02-16 scripts/03_clustering.Rmd
FIX rowMin and rowMax were wrong

```{r}
if(filter_genes){
    # Filter out q-values for the pvalues table
    col_to_keep = colnames(pvalues)[grepl("-pval", colnames(pvalues))]
    pvalues = pvalues[, col_to_keep]
    fishers_pval = moanin:::fisher_method(pvalues)
    genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}

@@

>>>>

```{r}
if(filter_genes){
    # First, filter out any genes that doesn't have a log fold change of at
    # least 2
    # XXX I should actually filter on the max, but it is broken right now.
    lfc_col_to_keep = colnames(pvalues)[
	grepl("-lfc_epicon", colnames(pvalues))]
    pvalues = pvalues[rowSums(abs(pvalues[, lfc_col_to_keep]) > 2) > 0, ]

    if(dim(pvalues)[1] > n_genes_to_keep){

	# Then rank by fisher's p-value and take max the number of genes of
	# interest
	# Filter out q-values for the pvalues table
	pval_col_to_keep = colnames(pvalues)[grepl("-pval", colnames(pvalues))]
	pvalues = pvalues[, pval_col_to_keep]
	fishers_pval = moanin:::fisher_method(pvalues)
    } else {
	genes_to_keep = names(pvalues)
    }
    genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}

@@

```{r results="hide", echo=FALSE}
# Save the clustering for the next step
write.table(labels, ".results/clustering_labels.txt", sep="\t")
```
